Text Technologies for Data Science Assignment 4

### 2014-11-17 tts4/report.tex
made tables smaller

% optionally, make links footnotes instead of hotlinks

% ams
\usepackage{amssymb,amsmath}

@@

After running the algorithm for 10 iterations, \texttt{klay@enron.com}
turned out to be the email address with the highest PageRank of
0.008027. Moreover, the email address in 6th place is
\texttt{kenneth.lay@enron.com} which is probably the email address of
the same person, CEO of Enron, Kenneth Lay. We can thus conclude that
the PageRank algorithm did quite well in figuring out who the
influential people are.

@@

After running the algorithm for 20 iterations,
\texttt{pete.davis@enron.com} turned out to be the email address with
the highest hub score of 0.999281. This is consistent with his role
description in \texttt{roles.txt} - broadcast proxy for auto-generated
emails. Other than that there were no abnormalities. Email addresses
with top 5 hub scores and top 5 authority scores are in tables 1 and 2,
respectively.

\begin{longtable}[c]{@{}ll@{}}
\toprule\addlinespace
\begin{minipage}[b]{0.37\columnwidth}\raggedright
Email
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright
Hub score
\end{minipage}
\\\addlinespace
\midrule\endhead
\begin{minipage}[t]{0.37\columnwidth}\raggedright
pete.davis@enron.com
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.999281
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.37\columnwidth}\raggedright
bill.williams@enron.com
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.032970
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.37\columnwidth}\raggedright
rhonda.denton@enron.com
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.010408
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.37\columnwidth}\raggedright
l..denton@enron.com
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.006774
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.37\columnwidth}\raggedright
grace.rodriguez@enron.com
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.005825
\end{minipage}
\\\addlinespace
\bottomrule
\addlinespace
\caption{Top 5 Hub scores}
\end{longtable}

\begin{longtable}[c]{@{}ll@{}}
\toprule\addlinespace
\begin{minipage}[b]{0.34\columnwidth}\raggedright
Email
\end{minipage} & \begin{minipage}[b]{0.17\columnwidth}\raggedright
Auth score
\end{minipage}
\\\addlinespace
\midrule\endhead
\begin{minipage}[t]{0.34\columnwidth}\raggedright
ryan.slinger@enron.com
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.384187
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.34\columnwidth}\raggedright
albert.meyers@enron.com
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.384177
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.34\columnwidth}\raggedright
mark.guzman@enron.com
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.383849
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.34\columnwidth}\raggedright
geir.solberg@enron.com
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.383764
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.34\columnwidth}\raggedright
craig.dean@enron.com
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.355581
\end{minipage}
\\\addlinespace
\bottomrule
\addlinespace
\caption{Top 5 Auth scores}
\end{longtable}

@@

I visualized connections between 10 people with the highest PageRank. I
used the \href{https://networkx.github.io}{networkx library} to create a
graph of these connections.

I used information from \texttt{roles.txt} to assign names and roles to
email accounts of Enron employees. Furthermore, the number of emails
exchanged between two people is displayed at the tail of an edge in red
color.

>>>>

% optionally, make links footnotes instead of hotlinks
% 
% ams
\usepackage{amssymb,amsmath}

@@

After running the algorithm for 10 iterations, \texttt{klay@enron.com}
turned out to be the email address with the highest PageRank of
0.008027. Moreover, the email address in 6th place is
\texttt{kenneth.lay@enron.com} which is probably the email address of
the same person, CEO of Enron, Kenneth Lay. We can thus conclude that
the PageRank algorithm did quite well in figuring out who the
influential people are. The top 5 PageRanks can be found in table 1.

@@

After running the algorithm for 20 iterations,
\texttt{pete.davis@enron.com} turned out to be the email address with
the highest hub score of 0.999281. This is consistent with his role
description in \texttt{roles.txt} - broadcast proxy for auto-generated
emails. Other than that there were no abnormalities. Email addresses
with top 5 hub scores and top 5 authority scores are in tables 2 and 3,
respectively.

\begin{longtable}[c]{@{}ll@{}}
\toprule\addlinespace
\begin{minipage}[b]{0.24\columnwidth}\raggedright
Email
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright
Hub score
\end{minipage}
\\\addlinespace
\midrule\endhead
\begin{minipage}[t]{0.24\columnwidth}\raggedright
pete.davis
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.999281
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.24\columnwidth}\raggedright
bill.williams
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.032970
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.24\columnwidth}\raggedright
rhonda.denton
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.010408
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.24\columnwidth}\raggedright
l..denton
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.006774
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.24\columnwidth}\raggedright
grace.rodriguez
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.005825
\end{minipage}
\\\addlinespace
\bottomrule
\addlinespace
\caption{Top 5 Hub scores}
\end{longtable}

\begin{longtable}[c]{@{}ll@{}}
\toprule\addlinespace
\begin{minipage}[b]{0.21\columnwidth}\raggedright
Email
\end{minipage} & \begin{minipage}[b]{0.17\columnwidth}\raggedright
Auth score
\end{minipage}
\\\addlinespace
\midrule\endhead
\begin{minipage}[t]{0.21\columnwidth}\raggedright
ryan.slinger
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.384187
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.21\columnwidth}\raggedright
albert.meyers
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.384177
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.21\columnwidth}\raggedright
mark.guzman
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.383849
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.21\columnwidth}\raggedright
geir.solberg
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.383764
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.21\columnwidth}\raggedright
craig.dean
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.355581
\end{minipage}
\\\addlinespace
\bottomrule
\addlinespace
\caption{Top 5 Auth scores}
\end{longtable}

@@

I visualised connections between 10 people with the highest PageRank. It
seemed that the algorithm ranked people with great influence highly and
thus visualising their connections could provide some additional
information about the scandal. I used the networkx library\footnote{NetworkX,
  https://networkx.github.io} to create a graph of these connections
which is then outputted into a file \texttt{graph.dot} and visualised
with graphviz.\footnote{graphviz, http://www.graphviz.org}

I used information from \texttt{roles.txt} to assign names and roles to
email accounts of Enron employees. Furthermore, the number of emails
exchanged between two people is displayed at the tail of an edge in red
colour.

My algorithm does not require any additional manual tuning which means
that it is very automatic but that it is also quite simple.
